---
title: "Min_Wen_Yang_scriptP2"
author: "1882252 Min Wen Yang"
date: "2022-09-22"
output: html_document
---
```{r results = "hide", message = F}
library(ggplot2)
library(GGally)
```
## Exercise 1
### 1.

```{r results = "hide", message = F}
library(foreign)
spssdata <- read.spss("SPSSData.sav")
```

### 2.

```{r results = "hide", message = F}
library("readxl")

importExceldata <- read_excel("ExcelData.xls")
```

## Exercise 2
### 1. Apparently the results are not equal. Can you explain this and how much is the difference? (hint: think about binary representation of integers and floating point numbers).
```{r}
sqrt(2) * sqrt(2) == 2
```

This is because sqrt(2) is a floating point. So two floating points' product is still a floating point. So that's why sqrt(2) * sqrt(2) == 2 returns FALSE.

### 2. Find a solution for this problem. Hint: look at in-built functions round(), all.equal().
```{r}
round(sqrt(2) * sqrt(2), digits = 0) == 2

all.equal(sqrt(2) * sqrt(2), 2)
```

solved.

### 3. Why is it important to be aware of this problem? Could you imagine a situation where you would need to take into account this issue? 
During calculating via R, we have to be aware of floating point problem. Because This will give you wrong output.

## Exercise 3.
### 1. 
```{r results = 'hide', message = F}
data(USArrests)
USArrests 
```

### 2.

[,1]	Murder	numeric	Murder arrests (per 100,000)\
[,2]	Assault	numeric	Assault arrests (per 100,000)\
[,3]	UrbanPop	numeric	Percent urban population\
[,4]	Rape	numeric	Rape arrests (per 100,000)

### 3.
```{r}
summary(USArrests)
```

it provides each variable's minimum/maximum value, median, mean, 1st & 3rd quantile.

### 4.
```{r}
ggpairs(USArrests)
```

It is clear that the correlation between "Assault" & "Murder" is the highest(0.802). There are some relation between "Rape"&"Murder", "Rape"&"Assault" to some extent.

```{r}
panel.hist <- function(x, ...)
{
  usr <- par("usr")
  par(usr = c(usr[1:2], 0, 1.5) )
  h <- hist(x, plot = FALSE)
  breaks <- h$breaks; nB <- length(breaks)
  y <- h$counts; y <- y/max(y)
  rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
}
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
  par(usr = c(0, 1, 0, 1))
  r <- abs(cor(x, y))
  txt <- format(c(r, 0.123456789), digits = digits)[1]
  txt <- paste0(prefix, txt)
  if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
  text(0.5, 0.5, txt, cex = cex.cor * r)
}

pairs(USArrests, diag.panel = panel.hist, upper.panel = panel.smooth, lower.panel = panel.cor)
```

### 6.
```{r}
library(lattice)

splom(~USArrests)
```

### 7.
```{r}
splom(~USArrests | state.region)
```

## Exercise 4.
```{r}
load("ChildIQ.RData")
```

### 1.
```{r}
summary(ChildData) 
```

This shows the mean, median, minimum/maximum value, 1st & 3rd quantile of each variables.
```{r}
dim(ChildData)
```

This shows the numbers of the observation and the number of the variable.
```{r}
str(ChildData)
```

This shows the structure of the data.
```{r}
head(ChildData)
```

This shows the top 6 observations of the data.


### 2.
```{r}
plot(ChildData$mom.iq, ChildData$kid.score, pch = 20, col = "darkblue")
```

### 3.
```{r}
plot(ChildData$mom.iq, ChildData$kid.score, pch = 20, col = "darkblue", xlab = "IQ of the mother", ylab = "child's score")
```

### 4.
```{r}
plot(ChildData$mom.iq, ChildData$kid.score, pch = 1, col = "darkgrey", xlab = "IQ of the mother", ylab = "child's score")
```

### 5.
```{r}
plot(ChildData$mom.iq, ChildData$kid.score, pch = 1, col = "darkgrey", xlab = "IQ of the mother", ylab = "child's score", 
     abline(lm(ChildData$kid.score~ChildData$mom.iq), lwd = 2, col = "red"))
```

### 6.
```{r}
plot(ChildData$mom.iq, ChildData$kid.score, pch = 1, col = "darkgrey", xlab = "IQ of the mother", ylab = "child's score", 
     abline(lm(ChildData$kid.score~ChildData$mom.iq), lwd = 4, col = "blue"))
```